Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-23 NEUROC/sec4-experiments.tex
更新sample size对accuracy的影响.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
    \caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
    \label{fig:exp_hyperparameter_accuracy_gat_small_info}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
    \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
    \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
\end{figure}

The relationship between the batch size and the accuracy was complex.
%
With the change of batch size, the accuracy relationship between GNNs is roughly the same.
%
For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
%
But there was also a little exceptions (cluster sampler on \texttt{amc}, relative batch size was 50\%).
%
To a certain extent, the increase of batch size could bring benefits to all GNNs.
%
However, for different datasets, the accuracy relationship between GNNs was not constant.
%
And this relationship was not related to model complexity.
%
In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
%
For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
%

When the batch size was small, as the batch size increased, the accuracy and the batch size would be positively correlated. 
%
However, when the batch size increases to a certain extent, there was no direct relationship between accuracy and batch size.
%
In other words, for sampling techniques, the batch size corresponding to the best accuracy may not be the maximum value, but may be another value. 
%
This phenomenon is consistent with the results in \cite{zeng2020_graphsaint}.

%
After using the sampling techniques, the optimal accuracy of some GNNs on certain datasets exceeded the accuracy of the full-batch training (neigbbor sampler on \texttt{amc}).
%
This showed that the application of sampling technology was very meaningful, because it may brought certain benefits to accuracy.
%
Different sampling techniques bring different gains to GNNs.
%

% added by wangyunpan, 2020-12-23, ----end----

>>>>

%\begin{figure}[H]
    %\centering
    %\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
    %\caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
    %\label{fig:exp_hyperparameter_accuracy_gat_small_info}
%\end{figure}

@@

\begin{figure}[H]
    \centering
    \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
    %
    \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
    %
    \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
    \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
    \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
\end{figure}

The experimental results confirmed the effectiveness of the sampling methods in terms of model accuracy.
%
When the relative batch size was greater than or equal to 3\%, the accuracy of the model trained by sampling was close to the accuracy obtained by full-graph training.
%
In most cases, the accuracy achieved by the sampling methods was slightly lower than the full-graph training.
%
However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}), the accuracy achieved by sampling methods was even higher.

The relationships between batch size and accuracy were complex.
%
A large batch size did not always bring high accuracy.
%
For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} decreased as the batch size increased.
%
A small batch size sometimes could achieve higher accuracy.
%
For example, in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}, the accuracy of GAT under 1\% relative batch size was even higher than the accuracy of the full-graph training.
%
Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
%
Our observations were similar to \cite{zeng2020_graphsaint}.
%
How to automatically select the proper batch size is a topic worth further studying.

Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
%
With the cluster sampler, the model accuracy of different GNNs was very close to the accuracy of full-graph training.
%
With the neighbor sampler, the model accuracy of different GNNs showed more obvious differences.
